\documentclass[]{resume}

\usepackage{makecell}
\usepackage{geometry}
\usepackage{etoolbox}
\usepackage{fancyhdr}
\usepackage{graphicx}

\pagestyle{fancy}
\fancyhf{}

\newtoggle{coop}
\toggletrue{coop}
%\togglefalse{coop}

\usepackage{tikz}

\iftoggle{coop}{
    \include{headers/coop/coopHeader}
}{
    \include{headers/name/nameHeader}
}

\begin{document}
\section*{Technical Skills}

{\renewcommand{\arraystretch}{1.5}%
\begin{tabular}{ll}
  \textbf{Programming:} & Python (5yr), JavaScript (3yr), TypeScript (1yr), Java (1yr), Go  \\
  \textbf{Tools:} & \makecell[l]{Git (3yr), Bash (2yr), Docker (2yr), Kubernetes} \\
  \textbf{Environment:} & Visual Studio Code (3yr), WebStorm (1yr), Postman (2yr) \\
  \textbf{Clouds:} & Microsoft Azure, Amazon Web Services \\
  \textbf{Testing:} & JUnit, JestJS \\
  \textbf{Web:} & Node.js (1yr), REST \\
\end{tabular}} 

\section*{Experience}
\experience{BGC Engineering}{DevOps Engineer Co-op}{Vancouver, Canada}{Jan 2022 – Present}{
  \item Updated Helm charts and worked with Azure DevOps pipelines to configure the automatic redeployment of applications onto a new Kubernetes cluster.
  \item Configured a compute-optimized Kubernetes cluster for a high-throughput tile rendering app.
  \item Templated Docker caching for use in pipelines with Azure ephemeral agents by configuring inline caching and pulling from a private Docker registry.
  \item Worked with AWS to configure a ECS cluster with Fargate backend for use with Dask to allow for computation of data ‘close to the source’.
}
\experience{Engel \& Völkers}{Freelance Data Analyst}{Nassau, Bahamas}{Dec 2018 – Jan 2021}{
  \item Reverse-engineered the housing market listing website API endpoints with Postman to develop a web scraper in Python which automated the filtering and downloading of housing data.
  \item Paired the web scraper with a data analysis algorithm written in R to clean, format and transpose the downloaded data into the required format, then exported to CSV files. These two are being used annually to generate housing market reports.
  \item Similarly, reverse-engineered the AirDNA website to scrape and download Airbnb \& Vrbo rental data in The Bahamas.
}

\section*{Technical Projects}
\project{Mangathr (TypeScript/Node.js)}{Apr 2021 – Present}{
  \item	Developed a CLI application, written in TypeScript and run with Node.js, which supports downloading and registering comics from various different sources.
  \item Wrote plugins for different websites, scraping the HTML or using the API to extract the relevant chapter images.
  \item Implemented a SQLite3 database to allow registration of multiple comics and automated checking for new chapters.
  \item Implemented a download system that asynchronously download images for each chapter.
}

\pagebreak

\project{Homelab (Bash/Docker)}{Jan 2020 –  Present}{
  \item	Deployed a Proxmox hypervisor on a dedicated machine and created an OPNSense VM, a dnsmasq LXC and a Ubuntu VM.
  \item Configured the OPNSense VM with OpenVPN and Wireguard connected to an Oracle Cloud VM running as a bastion server.
  \item Deployed multiple Docker containers running services, accessible via a Traefik reverse proxy.
}
\project{HealthIO (Java)}{Jan – Apr 2021}{
  \item	Developed mental health tracking desktop application with a Swing GUI.
  \item Implemented the ability to track two daily mental health scores, the daily sleep hours and assign activities to a day. 
  \item Created a visualization engine to display user data over a week duration. User data can be exported into CSV format.
  \item Made user data persistent by reading and writing data to a JSON file when the program is started/stopped.
  \item Testing for all non-UI code runs with 100\% code coverage.
}
\project{FruitTycoon (Python)}{Jan – May 2019}{
  \item	Created a multiplayer tycoon game in Python using the Discord.py library, in which players can make progress in text channels.
  \item Implemented a system which created user JSON files containing statistics and upgrades when player first interacts the channel bot.
  \item Developed three types of user-selectable fruit, and assigned higher monetary value to mixed fruit products, encouraging player cooperation.
  \item Made a leaderboard system, which searches through user JSON files every midnight, displaying the highest ranked players.
}

\section*{Extracurricular Activities}
\activity{Hack<IT> Design Competition \& Hack-a-thon}{Nassau, Bahamas}{Jul 2018}{
  \item	Brainstormed an idea to install front-facing cameras on a car to warn of incoming potholes.
  \item Prototyped using an Arduino and ultrasonic sensors, written in C++ to calculate distance.
  \item Presented our idea and prototype, which won our group \$2000 for the second year.
}
\activity{Hack<IT> Design Competition \& Hack-a-thon}{Nassau, Bahamas}{Jul 2017}{
  \item	Designed the outline of a product, installable on older cars which connects to a mobile network and adds capabilities, such as Bluetooth connectivity, remote start and pre-cooling.
  \item Developed a prototype with an Arduino which ran a HTTP server connected via Wi-Fi to remotely operate a servo; demonstrating remotely opening a car window.
  \item Presented our idea and prototype to an audience of tech CEO’s, which won our group \$2000.
}

\section*{Education}
\quad UBC Bachelor of Science in Computer Science
\hfill (Expected Graduation Date: Apr 2024)\\
\null\quad UBC Outstanding International Student Award
\hfill Sep 2020\\
\null\quad UBC Computer Science Tri-Mentoring 
\hfill Aug 2021\\

\end{document}
